%Creating a resume in LaTeX is a popular choice because it allows for highly customizable formatting and professional-looking documents. Here's a step-by-step guide along with a sample resume template in LaTeX.
\documentclass[a4paper,10pt]{article}  % Document class and font size
\usepackage[utf8]{inputenc}             % Input encoding
\usepackage{geometry}                   % Page layout
\usepackage{enumitem}                   % For custom list styles
\geometry{margin=1in}                   % 1-inch margins
\usepackage{hyperref}                   % For hyperlinks

% Custom commands for section headers
\newcommand{\ressection}[1]{\section*{\large \textbf{#1}}}
\newcommand{\resitem}[1]{\item \textbf{#1}}

\begin{document}
	
	% Header: Name and Contact Information
	\begin{center}
		{\Huge \textbf{Your Name}} \\
		Email: \href{mailto:yourname@email.com}{yourname@email.com} \\
		Phone: (123) 456-7890 \\
		LinkedIn: \href{https://www.linkedin.com/in/yourprofile}{linkedin.com/in/yourprofile} \\
		GitHub: \href{https://github.com/yourusername}{github.com/yourusername}
	\end{center}
	
	% Objective Section
	\ressection{Objective}
	A highly motivated software engineer with 3 years of experience in web development, seeking a challenging role in a dynamic organization to contribute to impactful projects.
	
	% Education Section
	\ressection{Education}
	\begin{itemize}[left=0pt]
		\resitem{Master of Science in Computer Science} \hfill 2020 -- 2022 \\
		University of XYZ, City, Country \\
		\textit{GPA: 3.8/4.0}
		
		\resitem{Bachelor of Technology in Information Technology} \hfill 2016 -- 2020 \\
		ABC Institute of Technology, City, Country \\
		\textit{GPA: 3.6/4.0}
	\end{itemize}
	
	% Work Experience Section
	\ressection{Work Experience}
	\begin{itemize}[left=0pt]
		\resitem{Software Engineer, ABC Tech} \hfill June 2022 -- Present \\
		Responsibilities:
		\begin{itemize}
			\item Developed and maintained RESTful APIs using Python and Django for an e-commerce platform.
			\item Improved website performance by 20\% through code optimization and database indexing.
			\item Worked in an agile team to deliver bi-weekly software updates.
		\end{itemize}
		
		\resitem{Web Developer Intern, XYZ Solutions} \hfill June 2020 -- May 2022 \\
		Responsibilities:
		\begin{itemize}
			\item Designed and implemented front-end components using HTML, CSS, and JavaScript.
			\item Integrated APIs for real-time data and user authentication.
			\item Collaborated with the design team to ensure responsive design on mobile platforms.
		\end{itemize}
	\end{itemize}
	
	% Projects Section
	\ressection{Projects}
	\begin{itemize}[left=0pt]
		\resitem{E-commerce Website} \hfill GitHub Link: \href{https://github.com/yourusername/ecommerce}{https://github.com/yourusername/ecommerce} \\
		Developed a full-stack e-commerce web application using Django (back-end) and React (front-end). Implemented payment gateway integration, user authentication, and product reviews.
		
		\resitem{AI-Powered Chatbot} \hfill GitHub Link: \href{https://github.com/yourusername/chatbot}{https://github.com/yourusername/chatbot} \\
		Built a chatbot using Python and NLP techniques to assist customers with product queries and support. Deployed on a cloud platform.
	\end{itemize}
	
	% Skills Section
	\ressection{Skills}
	\begin{itemize}[left=0pt]
		\item Programming Languages: Python, JavaScript, Java, C++
		\item Web Development: HTML, CSS, React, Node.js, Django
		\item Database: MySQL, PostgreSQL, MongoDB
		\item Tools: Git, Docker, Jenkins, AWS
		\item Other: Agile methodology, RESTful APIs, Test-Driven Development
	\end{itemize}
	
	% Certifications Section
	\ressection{Certifications}
	\begin{itemize}[left=0pt]
		\item AWS Certified Solutions Architect
		\item Certified Scrum Master (CSM)
	\end{itemize}
	
	% References Section
	\ressection{References}
	Available upon request.
	
\end{document}
